%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Technical Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cvtechentry
    {Collaborative Decision Making Maritime Prototype} % Job title
    {} % Leave Blank
    {} % Leave Blank
    {May. 2015 - Sept. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Analyzed customer needs, including overall port consumption, resulting in an efficient port emission and cost control solution.}
        \item {Applied software practices, such as agile methodology techniques, leading to a working prototype within 5 days.}
        \item {Facilitated daily scrums as scrum master, improving communication and allowing for concise meetings within a span of 15 minutes.}
        \item {Runner up to company hackathon for proposed product as a hot solution for efficient maritime business.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cvtechentry
    {Image Processing Remote Control Pi Car} % Job title
    {} % Leave Blank
    {} % Leave Blank
    {Mar. 2015 - Jun. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Lead a team of computer engineers using management applications, such as trello and slack, resulting in 2 additional software features implemented before deadline.}
        \item {Implemented algorithms solving communication between FPGA and raspberry pi, leading to successful GPIO data communication.}
        \item {Optimized bit transfer rate through advanced communication implementations, resulting in a speed increase of 6 frames per second.}
        \item {Demonstrated iterative testing cycles, reducing risk of wasted time and feature creep.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cvtechentry
    {Wheel of Lunch Github Contribution} % Job title
    {} % Leave Blank
    {} % Leave Blank
    {Nov. 2014 - Dec. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Collaborated on a RESTful web application aimed at implementing a front-end click and drag on wheel enhancement.}
        \item {Demonstrated complex problem solving skills, such as debugging and abstract modeling, leading to 3 bug fixes and 2 extra enhancements within 2 weeks.}
        \item {Executed self-taught knowledge of HTML5, CSS, and Javascript, leading to a fully operational system as an end result.}
        \item {Pull request successfully accepted and now shown on main website and Github repository.}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
