%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Junior Software Engineer} % Job title
    {Saab Technologies Ltd.} % Organization
    {British Columbia, Canada} % Location
    {May. 2015 - Sept. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Created and integrated starter development documents into media wiki, improving performance of new employees from 2 weeks to 2 days.}
        \item {Composed modular reports used by customers, leading to an overall customer satisfaction rating above 92\%.}
        \item {Proposed algorithms used to solve automation and emailing of crucial maritime information.}
        \item {Analyzed performance by managing and reviewing time spent on programming tasks using JIRA, resulting in an increased performance of 20\%.}
        \item {Applied  software engineering techniques, such as modularity and use cases, improving the existing solid n-tier architecture product.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Computer Engineer Assistant} % Job title
    {Computer for Schools} % Organization
    {British Columbia, Canada} % Location
    {March 2012 - April. 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Administered the distribution of refurbished computers resulting in 3,000 shipments and highest shipment of the year.}
        \item {Accomplished highest shipment mark in history of organization leading to over 1,000,000 computers shipped overall.}
        \item {Proposed communication line resulting in roughly 60 shipments being completed within 2 days.}
        \item {Completed inventory count ending with 158 laptops and 215 desktops counted in 30 minutes.}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
