%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-skyblue}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
% \photo[rectangle,edge,right]{./examples/profile}
\name{Michael}{Cao}
\position{Software Engineer}
\address{3050 Astor Drive, Burnaby, British Columbia, Canada, V3J 1K3}

\mobile{(+1)778-835-9953}
\email{michael.cao@alumni.ubc.ca}
\github{expensivecow}
\skype{michael.nam.cao}
% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
% \reddit{reddit-id}
% \extrainfo{extra informations}

%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
  {Telus Recruitment Team}
  {Telus Corporation.\\4535 Canada Way\\Burnaby, BC V5G 4P3}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Job Application for Software Engineer}
% How the letter is opened
\letteropening{Dear Sir/Madam}
% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter
\letterenclosure[Attached]{Curriculum Vitae}


%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[C]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {\today}
  {Michael Cao~~~·~~~Cover Letter}
  {}

% Print the title with above letter informations
\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}
The experts at Telus have shown, time and again, their ability to produce leading edge services combined with a great user interface. As a self-adapting motivated individual who understands a user interface in development is a key component to client driven business, I pursue the opportunity to improve and collaborate on bettering those who rely on Telus services. My ambition to keep up with the latest technologies and passion to contribute towards the growth of your company makes me a strong candidate for this position.

Efforts have also been taken outside of my life, within social coding mediums such as Github, to increase my knowledge about programming. I have actively joined projects to gain a wide variety of programming techniques and wealth of education that can only be gained from experience—Qualities I feel, many inexperienced developers will not have. Contributing to ongoing projects such as the Wheel of Lunch, a RESTful web application using primarily HTML, CSS, JavaScript, and Google Places API, to randomly select a restaurant within a fixed radius of your location, has sharpened my ability to self-learn and adapt to other user environments. Additionally, I pride myself, as an upcoming developer, in using the most commonly used processes in the industry to ensure high quality code is produced. Most notably, I effectively applied common agile practices such as test driven development, refactoring, and abstract modeling to a project known as JPacman, a pacman framework written in java. Using common tools, learned both from social coding and research, resulted in an overall test coverage of 91.7 percent and increase of 6 percent before refactoring.

I have also made efforts to get involved in life outside of university. In addition to participating in many large scale events, such as the Yonex Canada Open and British Columbia Conservatory of Music’s Music Festivals, I have accumulated over 1000 hours of volunteer experience. In particular, I previously volunteered as Burnaby North Secondary School’s badminton coach.  In this role, I was responsible for a multitude of tasks including: team composition, practice management, drill preparation, student mentorship, and game analysis.  Coaching at Burnaby North, I highly believe, has improved my ability to work as a team, critically think, and understand deadlines –traits which are indispensible and not shown in many individuals. Furthermore, I have realistic expectations of the rigors working within a fast paced team environment and evident experience multi-tasking. 

Thank you for your consideration and I look forward to hearing from you in the near future to further discuss my qualification. To arrange an interview, please contact the Co-op Office at 604-822-6995 or coop.interviews@ubc.ca


\end{cvletter}


%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter informations
\makeletterclosing

\end{document}
